12th International Satisfiability Modulo Theories Competition (SMT-COMP 2017): Rules and Procedures

### 2017-04-26 rules/rules17.tex
Clarify soundness

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) sound solvers disagree on their result.  More specifically,
a solver (including a solver that was entered into the competition by
the organizers for comparison purposes) is \emph{sound} for a division
if its raw score (Section~\ref{sec:benchmark-scoring}) is of the form
$\langle 0, n, w, c\rangle$ for each benchmark in the division, i.e.,
if it did not produce any erroneous results.  Two solvers
\emph{disagree} on a benchmark if one of them reported \texttt{sat}
and the other reported \texttt{unsat}.  Only the remaining benchmarks
are used in the following computation of division scores.

>>>>

\header{Main track: removal of disagreements.}
%
Before division scores are computed for the main track, benchmarks
with unknown status are removed from the competition results if two
(or more) solvers that are sound on benchmarks with known status
disagree on their result.  More specifically, a solver (including a
solver that was entered into the competition by the organizers for
comparison purposes) is \emph{sound on benchmarks with known status}
for a division if its raw score (Section~\ref{sec:benchmark-scoring})
is of the form $\langle 0, n, w, c\rangle$ for each benchmark in the
division, i.e., if it did not produce any erroneous results.  Two
solvers \emph{disagree} on a benchmark if one of them reported
\texttt{sat} and the other reported \texttt{unsat}.  Only the
remaining benchmarks are used in the following computation of division
scores.
